Causal_Analysis_Paper

### 2022-05-29 PaperAnalysis.Rmd
Added the dataset's ressources on the cleaning script and an outline for the paper analysis in the .rmd file
Initial steps towards the description of the paper

---
title: "Causal_Analysis_Paper"
author: "Ángela Duarte Pardo"
date: "5/23/2022"
output: html_document
---

@@

##    Causal Design

@@

>>>>

---
title: "Causal_Analysis_Paper"
author: "Helena Bakic, Anna-Lisa Wirth, Ángela Duarte Pardo"
date: "5/23/2022"
output: html_document
---

@@

## Description of the original paper
Latt, Milner and Kavanagh present the results of their ecological study on the effects of abortion laws on maternal mortality in their paper "Abortion laws reform may reduce maternal mortality: an ecological study in 162 countries."

### Datasets
The authors used a time-indexed dataset of maternal mortality from 1985 to 2015

To assess the effect of flexibility of abortion laws on on maternal mortality, the authors create an aggregate flexibility index [1-7] calculated based on the sum of the grounds on which abortion is permitted in every country

Description of Covariates.

##    Causal Design of the original paper

@@

# References

## Original paper
- Latt, S.M., Milner, A. & Kavanagh, A.(2019) Abortion laws reform may reduce maternal mortality: an ecological study in 162 countries. BMC Women's Health 19, 1. https://doi.org/10.1186/s12905-018-0705-y

## Origital paper datasets
-   UN (2013). Population division. World Abortion policies 2013.  [Accessible here](https://www.un.org/en/development/desa/population/publications/policy/world-abortion-policies-2013.asp)

## Updated datasets
- WHO. (2022). Global Abortion Policies Worldwide. [Accessible here](https://abortion-policies.srhr.org/)

-

## Other Resources
